Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-04-07 ms.tex
beginning of Markov chain section became redundant following recent changes

As explained in $\S$\ref{sec:modeling}, the two free parameters in our 
per-pixel dust emission SED are the hot dust temperature $T_2$, which 
determines the shape of the SED, and the spectrum normalization. In practice,
the normalization is controlled via $\tilde{I}_{545}$, the amplitude of the 
model SED in MJy/sr at $\nu$ = 545 GHz. For each pixel, we run a 
Metropolis-Hastings Markov chain sampling the posterior probability as a 
function of the two parameters $\tilde{I}_{545}$ and $T_2$. For each pixel, we 
are sampling the posterior given by:

@@

>>>>

In our full-resolution fits, we use a MCMC approach to constrain the 
parameters $\tilde{I}_{545}$ and $T_2$. For each pixel, we run a 
Metropolis-Hastings Markov chain sampling the posterior probability as a 
function of the two parameters $\tilde{I}_{545}$ and $T_2$. More specifically, 
we are sampling the posterior given by:

@@

% be careful about notational consistency with e.g. tildes, etc.. in this sect
